Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2017-02-12 manuscript/ajps/reviews_response.md

[Addressed] Thanks!

I do not consider myself a methodologist as such; therefore I will comment from the point of view as a possible user of such a method in other substantive areas. Does the paper do enough scholarly contribution to the discipline to be accepted to the premier journal in political science?

Even though an informed reader familiar with the text analytics will be able to follow the analyses presented, since the submission is t AJPS as opposed to Pol Analysis, I think the authors need to revise it to a considerable degree so that a general political science practitioner interested in applying such methods in his or research will be able to follow. At the very least, the authors need to address and revise frequent methods-related jargon, e.g., "boiler plate removal" encountered in text. I am not sure an average reader of AJPS is familiar with it. I was also surprised that the authors omit several important references to applied text analytics in political science, such as those of Laver, Benoit, Garry 2003, Slapin and Proksch; Lowe; Grimmer, etc (I am not one of these authors and am not related to them, only think it is important to relate to the growing literature on political text so that this paper does not look like a niche paper but as a part of a growing
research program instead).

[Addressed] I added a couple of string cites to emphasize the broader connections and contributions we offer---both to the text as data methods literature and to any substantive applied work that involves analysis of text corpora.

@@

After reading the paper my overall impression is that it will be very suitable for a special volume on political text, or perhaps for a more specialized journal such as State Politics & Policy Quarterly. As it stands, I think it requires very considerable revisions to be considered for publication in AJPS.

[Addressed] OK

The authors do not introduce any new data - they rely on the existing dataset. They do not offer a new theory that explains the logic behind the re-use of legislative bills, whether based on interest groups literature or the diffusion literature, for example. As such, it is a measurement paper. The SW text re-use algorithm has been previously employed in Political Science in Wilkerson et al (2015), as the authors themselves acknowledge. The authors here re-use the same algorithm, with slight modifications to improve it.  On p. 11 they underline that "In our analyses we use a slightly modified version of the local alignment algorithm, in which the first gap in a series of multiple gaps receives a higher penalty then the following ones (Wilkerson et al., 2015, use the same modification)." "The idea behind this modification is that someone who changes text in a bill might insert several words into an existing piece of text."

[Addressed] I updated the conclusion to note that the all-bill-pairs database is a novel contribution, and that we will distribute it with the supplemental materials for this article.

### 2017-02-12 manuscript/main.tex
updated another point of R1's
addressed another R1 point

The alignment scores we derive provide a resource for scholars to test hypotheses of the causes and consequences of the introduction and adoption of similar policies---a measure which crosses different policy areas, states, and time. In a validation experiment, we show that a wide span of quantiles of alignment scores between bills---from the median up through and above the 99$^{th}$ percentile---are negatively correlated with the ideological distance between the legislators who introduced the two bills. This result opens the door to many other hypotheses that could be tested using alignment scores for bill pairs.  Where and when do similar policies cross state borders? Which legislators introduce similar legislation? Does lobbying by pressure groups result in the adoption of similar policies across states? Do similar patterns of campaign contributions to legislators predict similar policies in proposed legislation? Questions such as these can be directly investigated using the policy similarity measures we introduce.

>>>>

The alignment scores we derive provide a resource for scholars to test hypotheses of the causes and consequences of the introduction and adoption of similar policies---a measure which crosses different policy areas, states, and time. In a validation experiment, we show that a wide span of quantiles of alignment scores between bills---from the median up through and above the 99$^{th}$ percentile---are negatively correlated with the ideological distance between the legislators who introduced the two bills. This result opens the door to many other hypotheses that could be tested using alignment scores for bill pairs.  Where and when do similar policies cross state borders? Which legislators introduce similar legislation? Does lobbying by pressure groups result in the adoption of similar policies across states? Do similar patterns of campaign contributions to legislators predict similar policies in proposed legislation? Questions such as these can be directly investigated using the policy similarity measures we introduce. The alignment scores for all bill pairs---a novel database which we contribute---are available in the supplemental materials with this article. The validation exercises assure that researchers can use the alignment scores that we derive for our bill pairs database to study the policy similarity between bills at the level of bill pairs, or aggregated up to higher levels.
